---
title: "Shiny Project Reproducible Pitch"
author: "Stephanie Huffaker"
date: "April 30, 2017"
output: ioslides_presentation
smaller: true
---

```{r setup, include=FALSE, tidy = TRUE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)

```

## Purpose and Data {.smaller}

- This presentation is the companion to my Shiny project for the Developing Data Products class on Coursera as part of the Data Science Specialization.
- In this presentation, the process for creating the app along with some reproducible code will be provided.
- Shiny application can be found at: https://snhuffaker.shinyapps.io/ddp_shiny_project/
- Full code can be found at: https://github.com/snhuffaker/Developing-Data-Products/tree/gh-pages/Shiny
- It is currently National Hockey League (NHL) playoffs time here in the United States and I decided to use NHL statistics as the basis for my project. I found a downloadable data file online which contained a variety of statistics and chose to use the stats by team.
- After some preliminary data exploration, I decided to create a shiny app with a slider to choose a year to filter the data, some overal stats about that season, a plot of wins by team (sorted in decreasing order) and a dynamic table showing either the top 5 or bottom 5 teams that season with some additional statistics chosen by a radio button selector.
  
## Sample Plot {.smaller}

```{r echo = TRUE}
teams <- read.csv("Teams.csv")
input <- 2015
t <- teams[teams$year == as.character(input),]
t$name <- factor(t$name, levels = t[order(t$W, decreasing = TRUE),]$name)
p <- qplot(x = name, y = W, data = t) + ggtitle(paste(input," - ", input + 1, " Season Wins")) +
    xlab("Teams Ranked by # of Wins") + ylab("Wins") + theme(axis.text.x=element_text(angle=90, hjust=1, size = 12),
    axis.title=element_text(size=14, face = "bold"), plot.title=element_text(size=20, face = "bold"))
print(p)
```

## Sample ShinyUI Code {.smaller}

```{r echo = TRUE, eval = FALSE}
library(shiny)
shinyUI(fluidPage(
  # Application title
  titlePanel("NHL Team Statistics"),
  # Sidebar with drop down for team and slider for year
  sidebarLayout(
    sidebarPanel(
      sliderInput("season", "Use the slider to choose a year:", min = 1909, max = 2015, value = 2015, sep = ""),
      radioButtons("tb", "Choose whether to show Top 5 or Bottom 5 teams for the year", choices = c("Top 5", "Bottom 5"), selected = "Top 5"),
      textOutput("avgWins"),
      textOutput("avgPts"),
      textOutput("avgGF"),
      textOutput(""),
      textOutput(""),
      h3("Documentation:"),
      h4("This app contains data for all NHL seasons from 1909 to 2015. Use the slider to select a year to filter the data by season 
          and the radio button to select whether to show the top 5 or bottom 5 teams from that season")
    ),
  # Show a plot of the information selected and either top 5 or bottom 5 teams based on radio button selection
    mainPanel(
      plotOutput("winsPlot"),
      textOutput("tbhead"),
      tableOutput("topbot")
    )
  )
))

```

## Sample Shiny Server Code {.smaller}

```{r eval = FALSE, echo = TRUE}
library(shiny)
library(ggplot2)
teams <- read.csv("Teams.csv")
shinyServer(function(input, output, session) {
  output$winsPlot <- renderPlot({
    t <- teams[teams$year == as.character(input$season),]
    t$name <- factor(t$name, levels = t[order(t$W, decreasing = TRUE),]$name)
    p <- qplot(x = name, y = W, data = t) + ggtitle(paste(input$season," - ", input$season + 1, " Season Wins")) +
      xlab("Teams Ranked by # of Wins") + ylab("Wins") + theme(axis.text.x=element_text(angle=90, hjust=1, size = 12),
      axis.title=element_text(size=14, face = "bold"), plot.title=element_text(size=20, face = "bold"))
    print(p)})
  mwin <- reactive({
    t <- teams[teams$year == as.character(input$season),]
    mean(t$W)})
  output$avgWins <- renderText({
    paste("Average wins: ",round(mwin(),2))})
  mPts <- reactive({
    t <- teams[teams$year == as.character(input$season),]
    mean(t$Pts)runtime:shiny})
  output$avgPts <- renderText({
    paste("Average points: ",round(mPts(),2))})
  mGF <- reactive({
    t <- teams[teams$year == as.character(input$season),]
    mean(t$GF)})
  output$avgGF <- renderText({
    paste("Average goals for: ",round(mGF(),2))})
  output$tbhead <- renderText({
    paste(input$tb," teams")})
  tb <- reactive({
    as.logical(ifelse(input$tb == "Top 5",1,0))})
  output$tb <- renderText({
    tb()})
  output$topbot <- renderTable({
    t <- teams[teams$year == as.character(input$season),]
    topbot <- head(t[order(t$W, decreasing = tb()),],5)
    topbot <- topbot[,-c(1,2,3,4,5,6,7,8,15,16,20,21,22,23,24,25,26,27)]})
})
```

